\documentclass[12pt,a4paper]{book}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{draftwatermark}
\usepackage{textcomp}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 right=20mm,
 bottom=20mm,
 top=20mm,
 }
\date{25-09-2018}
\author{Philip Martin Taylor}
\title{TaylorWorld (Blerontin Castle 1)}
\begin{document}
\begin{center}
\textbf{TaylorWorld\texttrademark \: Blerontin Castle 1.}
\end{center}
\begin{flushleft}
  The party find themselves outside Blerontin castle, outside the tents they spent overnight in, where they hear in the distance a market inside the castle, with guards guarding the castle gates. Outside their tents they have a smouldering fire, a coffee pot, and some basic cooking kit, and some basic food stuffs in their tents which they could make for breakfast with. the castle is surrounded by medium density forests, with a variety of open clearings, which also contains some small cottages.
\end{flushleft}
\begin{flushleft}
  The party leaves their tents, finding a note outside their tents from an 8 month pregnant wizard called Nida Rorra, who is expecting a daughter, her daughters father is the Lord of Blerontin who kicked Nida out of the state rooms in the castle and left her destitute, asking the party if they could find the Lord of blerontin in his castle, and take him to the local police, where justice can be served.
\end{flushleft}
\begin{flushleft}
  The daughter of the pregnant wizard will be revisited at a later point, who will want revenge on her mother who abandoned her and asked for her father to be killed in an act of revenge.
\end{flushleft}
\begin{flushleft}
  The inside of the castle has a lawn with several stalls surrounding it. The outside of the castle has 7 turrets with walls surrounding it, and a moat, and several gates to be able to enter the castle which are accessible by draw bridges. Underneath the castle there are tombs, torture rooms, a prison and rooms filled with armour, weapons and other equipment. The castle also has a blacksmith, a brewery, 
\end{flushleft}
\begin{flushleft}
  The castle brewery makes a brew called, Blerontin Lemon Blast, which for 1d6 rounds causes a -1 wisdom penalty, a +1 charisma bonus, and slowed and sicked conditions, the fortitude save DC is 13.
\end{flushleft}
\begin{flushleft}
\item[$\bullet$ NPCS:] Guards(Thendra, Markle, Nordec), Nida Rorra(8 month pregnant wizard), Zara Rorra(wizards daughter), 'ogimi' Thenvir Ejag(lord of blerontin), Market stall Holders, 
  \item[$\bullet$ Traps:] Spiked Pit Trap, pit trap, poisoned arrow trap, arrow trap, scythe trap, 
\end{flushleft}
\begin{center}
  \textcopyright{} 2018 Philip Martin Taylor
\end{center}
\end{document}